The necessity of hypermedia RDF and an approach to achieve it

### 2012-04-13 eswc-2012/workshop2.tex
grammar
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@226 43ef1190-90fd-4dd7-a769-d0121f02b80e
third person
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@227 43ef1190-90fd-4dd7-a769-d0121f02b80e

This term is motivated by that POST operations in \cite{graphstore} is
specified to results in an RDF Merge of the payload into the named
graph. Amongst other possibilities is a union of graphs.

@@

Mike Amundsen solicits feedback on the completeness of his
classification scheme. I suggest the following as discussion items:

>>>>

This term is motivated by that POST operations in \cite{graphstore} are
specified to result in an RDF Merge of the payload into the named
graph. Amongst other possibilities is a union of graphs.

@@

Mike Amundsen solicits feedback on the completeness of his
classification scheme. The following are suggested as discussion
items:
